MS797

### 2022-01-31 _academics/ms797/ms797.Rmd
correct path

<p style="background: #eee">
Academics &gt; ML797
</p>

@@

- My ongoing [glossary](../ml797-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.

>>>>

<p style="background: #eee">
Academics &gt; MS797
</p>

@@

- My ongoing [glossary](../ms797-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.
